Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-06-19 arxiv/template.tex
refer to JOSE

We can use $u_1$ as a coordinate on the same footing as
circumferential radius $r$.  First we suppress $\theta,\phi$
coordinates and consider only $r,t$; see Figures~\ref{schwarzschild},
\ref{eddington}, and ~\ref{gullstrand}.

>>>>

We can use $u_1$ as a coordinate on the same footing as
circumferential radius $r$ and present a number of diagrams taken
from~\citep{hankin2020}.  Below, each figure has two parts: on the
left, we see the standard figure using circumferential radius $r$, and
on the right we see the same figure but with the horizontal axis
showing $u_1$.  First we suppress $\theta,\phi$ coordinates and
consider only $r,t$; see Figures~\ref{schwarzschild}, \ref{eddington},
and ~\ref{gullstrand}.
